Individual heterogeneity in the functional network topography of medial prefrontal cortex

### 2019-08-27 Manuscript.Rmd
added a missing ROI to the example analysis script

# raw counts for each area per literature
nRegions_sv <- do.call(rbind, studyList_sv) %>% count #(X1)
nRegions_DN <- do.call(rbind, studyList_DN) %>% count #(X1)
nRegions_all <- left_join(nRegions_sv, nRegions_DN, by = "X1")

@@

```{r Extra examples (supplemental fig 3), out.width = "100%", fig.align = "center", fig.cap = "Signal quality prior to FV thresholding. Left: Surface map displaying the vertex-wise mean tSNR across individuals. Right: Mean tSNR for mPFC and PCC across individuals."}
# To get the box plot:
#   
# allSnr <- list()
# 
# for (i in seq_along(Summaries)) {
#   
#   allSnr[[i]] <- Summaries[[i]] %>% 
#                   mutate(region = ifelse(y > 0, "mPFC", "PCC")) %>%
#                   group_by(region) %>%
#                   summarise(mtSNR = mean(tSNR))
#                 
# }
# 
# allSnr <- do.call(rbind, allSnr)
# 
# ggplot(data = allSnr, aes(region, mtSNR, fill = region)) + 
#   geom_boxplot(show.legend = F) +
#   scale_fill_manual(values = Cols[seq(2)]) +
#   labs(x = "", y = "mean tSNR") +
#   theme(legend.position = c(0.9, 0.32),
#         legend.key=element_blank(),
#         panel.grid.major = element_blank(),
#         panel.grid.minor = element_blank(),
#         panel.background = element_blank(),
#         axis.line = element_line(colour = "black"),
#         text = element_text(size = 22))

@@

>>>>

# raw counts for each area per literature
nRegions_sv <- do.call(rbind, studyList_sv) %>% count(X1)
nRegions_DN <- do.call(rbind, studyList_DN) %>% count(X1)
nRegions_all <- left_join(nRegions_sv, nRegions_DN, by = "X1")

@@

```{r tSNR (supplemental fig 3), out.width = "100%", fig.align = "center", fig.cap = "Signal quality prior to FV thresholding. Left: Surface map displaying the vertex-wise mean tSNR across individuals. Right: Mean tSNR for mPFC and PCC across individuals."}
# To get the box plot:
#   
# allSnr <- list()
# 
# for (i in seq_along(Summaries)) {
#   
#   allSnr[[i]] <- Summaries[[i]] %>% 
#                   mutate(region = ifelse(y > 0, "mPFC", "PCC")) %>%
#                   group_by(region) %>%
#                   summarise(mtSNR = mean(tSNR))
#                 
# }
# 
# allSnr <- do.call(rbind, allSnr)
# 
# ggplot(data = allSnr, aes(region, mtSNR, fill = region)) + 
#   geom_boxplot(show.legend = F) +
#   scale_fill_manual(values = Cols[seq(2)]) +
#   labs(x = "", y = "mean tSNR") +
#   theme(legend.position = c(0.9, 0.32),
#         legend.key=element_blank(),
#         panel.grid.major = element_blank(),
#         panel.grid.minor = element_blank(),
#         panel.background = element_blank(),
#         axis.line = element_line(colour = "black"),
#         text = element_text(size = 22))

@@

```{r extra B&B checks with silhouette (supplemental fig 4), out.width = "100%", fig.align = "center", fig.cap = "Additional checks to confirm the match between our findings with Braga & Buckner (2017)."}
# # produce the silhouette plot
# setwd('Silhouette')
# 
# # load data and get the overall plus mean (+SE) silhouette scores per cluster x subject
# files <- list.files()
# data <- lapply(files, read_csv) %>% reduce(full_join)
# data2 <- data %>% 
#   group_by(Clusters) %>%
#   summarise(mSil = mean(Silhouette),
#             seSil = sd(Silhouette) / sqrt(length(Silhouette)))
# 
# # plot
# ggplot() +
#   geom_line(data = data, aes(Clusters, Silhouette, group = SubjID), show.legend = F, alpha = 0.09, size = 1.5) +
#   geom_point(data = data2, aes(Clusters, mSil), show.legend = F, size = 2) +
#   geom_errorbar(data = data2, aes(Clusters, ymin = mSil - seSil, ymax = mSil + seSil), width = 0.1, size = 1) +
#   labs(x = "Number of Clusters", y = "Silhouette Score") +
#   theme(legend.key = element_blank(),
#         panel.grid.major = element_blank(), 
#         panel.grid.minor = element_blank(), 
#         panel.background = element_blank(), 
#         axis.line = element_line(colour = "black"),
#         text = element_text(size = 22))
